### 2021-07-31 paper.tex
changed document type to report and most sections to chapters

\documentclass[11pt]{article}

% fonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{tgschola}
\usepackage{inconsolata}
\usepackage{amsmath}

% images
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{wrapfig}

% page border
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{eso-pic}

% spacing in certificate
\usepackage{changepage}
\usepackage{setspace}

% code listing
\usepackage{minted}
\usemintedstyle{tango}

% sections on new page
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}
%\setcounter{secnumdepth}{0}

% index and clickable toc
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

% bibliography
\usepackage{bookmark}
\usepackage{url}
\usepackage[
	backend=biber,
	style=numeric,
	%citestyle=ieee
]{biblatex}
\usepackage{csquotes}

\addbibresource{bibliography.bib}

% table of content name
%\usepackage[nottoc]{tocbibind}
%\renewcommand{\theHsection}{\thepart.section.\thesection}
%\addto\captionsenglish{% Replace "english" with the language you use
	%\renewcommand{\contentsname}%
	%{\hfill \Huge Table of Content \hfill}%
%}

@@

	% abstract
	\section[abstract]{Abstract}

@@

	\thispagestyle{plain}
	\begin{center}
		\Large
		\textbf{Brain Tumor Detection}

		\vspace{0.4cm}
		\large
		Using various machine learning models to detect brain tumor.
	\end{center}

@@

	\begin{enumerate}
		\item \textbf{ Data collection }
		\item \textbf{ Pre-processing }
		\item \textbf{ Average filtering }
		\item \textbf{ segmentation }
		\item \textbf{ feature extraction }
		\item \textbf{CNN (or any other model) via classification and identification. By
			utilizing the DM (data mining) techniques, significant relations and
			patterns from the data can be extracted. The techniques of ML
			(machine learning) and Data mining are being effectively employed
			for brain tumor detection and prevention at an early stage.}
	\end{enumerate}

	\section[introduction]{Introduction}
	\subsection[domain description]{Domain Description}

@@

	\subsection[motivation]{Motivation}
	The motivation is to develop a software with better segmentation capability
	for use in medical imaging to detect diseases like brain tumor. Image
	segmentation has been identified as the key problem of medical image
	analysis and remains a popular and challenging area of research. Image
	segmentation is increasingly used in many clinical and research applications
	to analyze medical imaging datasets; which motivated us to present a
	snapshot of dynamically changing field of medical image segmentation.

@@

	\subsection[scope of work]{Scope of Work}
	\subsubsection[deliverables]{Deliverables}
	\begin{itemize}
		\item Working program to take an MRI scan as input and predict presence
			of tumorous cells with $\geq 90\%$ accuracy.
	\end{itemize}

	\subsubsection[scope]{Scope}
	\begin{itemize}
		\item The working program has external dependencies ( libraries ) and
			it's expected to have a them installed for the program to work.
	\end{itemize}

@@

	\section[background]{Background}
	\input{backgournd.tex}

	\section[methodology]{Methodology}

@@

	\subsection{Image Acquisition}%
	\label{sub:Image Acquisition}

@@

	\subsection{Preprocessing}%
	\label{sub:Preprocessing}

@@

	\begin{figure}[H]
		\centering
		\subfloat[Original Image]
		{\includegraphics[width=0.2\linewidth]
		{imgs/Y100.JPG}\label{original}}
		\hspace{0.5cm}
		\subfloat[Filtered Imaage]
		{\includegraphics[width=0.2\linewidth]
		{imgs/median_filtering.png}\label{smooted image}}
		\hspace{0.5cm}
		\subfloat[Edge Detection]
		{\includegraphics[width=0.2\linewidth]
		{imgs/edges_detection.png}\label{edge detection}}
		\hspace{0.5cm}
		\subfloat[Segmentation]
		{\includegraphics[width=0.2\linewidth]
		{imgs/segmentation.png}\label{segmentation}}
		\caption{preprocessing operations}
		\label{Preprocessing Operations}
	\end{figure}

	\subsection{Feature Extraction}%
	\label{sub:Feature Extraction}

@@

	\subsection{Classification}%
	\label{sub:Classification}

@@

	\subsection{Convolutional Neural Network}%
	\label{sub:Convolutional Neural Network}

@@

	\subsection{VGG 16}

@@

	\subsubsection{Architecture}
	\label{sssec:vgg arch}

@@

	\subsubsection{Configuration}

	The ConvNet configurations, evaluated in this paper, are outlined in
	Figure~\ref{fig:vgg16_conf}, one per column. In the following we will refer
	to the nets by their names (A–E).  All configurations follow the generic
	design presented in Section~\ref{sssec:vgg arch} and differ only in the
	depth: from 11 weight layers in the network A (8 conv. and 3 FC layers) to
	19 weight layers in the network E (16 conv. and 3 FC layers). The width of
	conv. layers (the number of channels) is rather small, starting from 64 in
	the first layer and then increasing by a factor of 2 after each max-pooling
	layer, until it reaches 512.
	\cite[3]{simonyan2015deep}

	\begin{figure}[h]
		\centering
		\includegraphics[width=\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

	\subsection{ResNet 50}%
	\label{sub:ResNet 50}

	\subsubsection{Residual Learning}

@@

	\subsubsection{Network Architecture}

@@

	\section[implementation]{Implementation}

	\subsection{Assumptions and Dependencies}%
	\label{sub:Assumptions and Dependencies}
	It is assumed that the MRI scans are collected and processed before feeding
	into the module.

@@

	\subsection{Implementation Methods}%
	\label{sub:Implementation Methods}
	After acquiring the data, the data is classified into two classes (binary
	class) of yes, consisting of tumorous cell and no, not consisting tumorous
	cells. A second batch of images is kept separate for prediction, the
	prediction batch.

@@

	After training is complete the models are then evaluated (further discussed
	in Section~\ref{sec:result} )

	\section[result]{Result}%
	\label{sec:result}

@@

	\section[appendix]{Appendix}%
	\label{sec:Appendix}

	\subsection{Tensorflow Implementation}%
	\label{sub:Tensorflow Implementation}

	\subsubsection{CNN}
	\input{tf_cnn.tex}

	\subsubsection{VGG 16}
	\input{tf_vgg.tex}

	\subsubsection{ResNet 50}
	\input{tf_reset.tex}

	\subsubsection{Prediction}
	\input{tf_prediction.tex}

	\subsection{fast.ai Implementation}%
	\label{sub:fast.ai Implementation}

	\subsubsection{CNN}
	\input{fastai_cnn.tex}

@@

	\subsubsection{VGG 16}
	\input{fastai_vgg.tex}

@@

	\subsubsection{ResNet 50}
	\input{fastai_resnet.tex}

>>>>

\documentclass[11pt]{report}

\input{imports.tex}

@@

	% abstract
	%\section[abstract]{Abstract}
	\chapter{Abstract}

@@

	\thispagestyle{plain}

@@

	\begin{enumerate}
		\item Data collection
		\item Pre-processing
		\item Average filtering
		\item Segmentation
		\item Feature extraction
		\item CNN (or any other model) via classification and identification. By
			utilizing the DM (data mining) techniques, significant relations and
			patterns from the data can be extracted. The techniques of ML
			(machine learning) and Data mining are being effectively employed
			for brain tumor detection and prevention at an early stage.
	\end{enumerate}

	\chapter{Introduction}
	\section[domain description]{Domain Description}

@@

	\section[motivation]{Motivation}
	The motivation is to develop a software with better segmentation capability
	for use in medical imaging to detect diseases like brain tumor. Image
	segmentation has been identified as the key problem of medical image
	analysis and remains a popular and challenging area of research. Image
	segmentation is increasingly used in many clinical and research applications
	to analyze medical imaging datasets; which motivated us to present a
	snapshot of dynamically changing field of medical image segmentation.

@@

	\section[scope of work]{Scope of Work}
	\subsection[deliverables]{Deliverables}
	\begin{itemize}
		\item Working program to take an MRI scan as input and predict presence
			of tumorous cells with $\geq 90\%$ accuracy.
	\end{itemize}

	\section[scope]{Scope}
	\begin{itemize}
		\item The working program has external dependencies ( libraries ) and
			it's expected to have a them installed for the program to work.
	\end{itemize}

@@

	\chapter{Background}
	\input{backgournd.tex}

	\chapter{Methodology}

@@

	\section{Image Acquisition}%

@@

	\section{Preprocessing}%

@@

	\begin{figure}[ht]
		\centering
		\subfloat[Original Image]
		{\includegraphics[width=0.2\linewidth]
		{imgs/Y100.JPG}\label{original}}
		\hspace{0.5cm}
		\subfloat[Filtered Imaage]
		{\includegraphics[width=0.2\linewidth]
		{imgs/median_filtering.png}\label{smooted image}}
		\hspace{0.5cm}
		\subfloat[Edge Detection]
		{\includegraphics[width=0.2\linewidth]
		{imgs/edges_detection.png}\label{edge detection}}
		\hspace{0.5cm}
		\subfloat[Segmentation]
		{\includegraphics[width=0.2\linewidth]
		{imgs/segmentation.png}\label{segmentation}}
		\caption{preprocessing operations}
		\label{Preprocessing Operations}
	\end{figure}

	\section{Feature Extraction}%

@@

	\section{Classification}%

@@

	\section{Convolutional Neural Network}%

@@

	\section{VGG 16}

@@

	\subsection{Architecture}
	\label{sec:vgg_arch}

@@

	\subsection{Configuration}

	The ConvNet configurations, evaluated in this paper, are outlined in
	Figure~\ref{fig:vgg16_conf}, one per column. In the following we will refer
	to the nets by their names (A–E).  All configurations follow the generic
	design presented in Section~\ref{sec:vgg_arch} and differ only in the
	depth: from 11 weight layers in the network A (8 conv. and 3 FC layers) to
	19 weight layers in the network E (16 conv. and 3 FC layers). The width of
	conv. layers (the number of channels) is rather small, starting from 64 in
	the first layer and then increasing by a factor of 2 after each max-pooling
	layer, until it reaches 512.
	\cite[3]{simonyan2015deep}

	\begin{figure}[ht]
		\centering
		\includegraphics[width=\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

	\section{ResNet 50}%

	\subsection{Residual Learning}

@@

	\subsection{Network Architecture}

@@

	\chapter{Implementation}

	\section{Assumptions and Dependencies}%
	It is assumed that the MRI scans are collected and processed before feeding
	into the module.

@@

	\section{Implementation Methods}%
	After acquiring the data, the data is classified into two classes (binary
	class) of yes, consisting of tumorous cell and no, not consisting tumorous
	cells. A second batch of images is kept separate for prediction, the
	prediction batch.

@@

	After training is complete the models are then evaluated (further discussed
	in Chapter~\ref{chap:Res} )

	\chapter{Result}
	\label{chap:Res}

@@

	\chapter{Appendix}

	\section{Tensorflow Implementation}%

	\section{CNN}
	\input{tf_cnn.tex}

	\section{VGG 16}
	\input{tf_vgg.tex}

	\section{ResNet 50}
	\input{tf_reset.tex}

	\section{Prediction}
	\input{tf_prediction.tex}

	\section{fast.ai Implementation}%

	\section{CNN}
	\input{fastai_cnn.tex}

@@

	\section{VGG 16}
	\input{fastai_vgg.tex}

@@

	\section{ResNet 50}
	\input{fastai_resnet.tex}
